---
title: "Analyses of famous mtcars dataset"
author: "Vinicius Lago"
date: "05/10/2020"
output: ioslides_presentation

---

```{r setup, include=FALSE }
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This document was created as a documentation of web app created in Developing Data Products Course Project.  

This web app was created based in famous **mtcars R dataset** to accomplish the Course Project.  

The goal of this panel is understand the relationship of some variables of the dataset, build with actual values for some types of cars.  

## Mtcars dataset

Let's visualize the summary of the variables of **mtcars** used in this app.  

```{r, echo = TRUE, warning = FALSE, comment=""}

summary(mtcars[, c("mpg", "cyl", "hp", "wt", "qsec")])

```


## Using the Panel

The panel consists of a sidebar and a graph.  

- Sidebar: in this place the user can choose the tow variables of interest. Click in **Submit button** to update the graph;  

- Graph: the user can see all actual values for the different types of cars (points) and a regression line representing the trend of the chosen data. 

## Thanks!!
